Lesson 4
========================================================

***

### Scatterplots and Perceived Audience Size
Notes:

***

### Scatterplots
Notes:

```{r Scatterplots}
library(ggplot2)
pf <- read.csv("pseudo_facebook.tsv", sep = '\t')
names(pf)
qplot(x = age, y = friend_count, data = pf)
qplot(age, friend_count, data = pf)
```

***

#### What are some things that you notice right away?
Response:

***

### ggplot Syntax
Notes:

```{r ggplot Syntax}

ggplot(aes(x = age, y = friend_count), data = pf) + geom_point() +
  xlim(13,90) 

summary(pf$age)
```

***

### Overplotting
Notes:

```{r Overplotting}
ggplot(aes(x = age, y = friend_count), data = pf) +
  geom_point(alpha = 1/20) +
  xlim(13,90)
```

```{r overplotting}
ggplot(aes(x = age, y = friend_count), data = pf) +
  geom_jitter(alpha = 1/20) +
  xlim(13,90)
```

#### What do you notice in the plot?
Response:

***

### Coord_trans()
Notes:

```{r Coord_trans()}
ggplot(aes(x = age, y = friend_count), data = pf) +
  geom_point(alpha = 1/20) +
  xlim(13,90) +
  coord_trans(y = "sqrt")
```


#### Look up the documentation for coord_trans() and add a layer to the plot that transforms friend_count using the square root function. Create your plot!

```{r}
ggplot(aes(x = age, y = friend_count), data = pf) +
  geom_point(alpha = 1/20, position = position_jitter(h = 0)) +
  xlim(13,90) +
  coord_trans(y = "sqrt")
```

#### What do you notice?

***

### Alpha and Jitter
Notes:

```{r Alpha and Jitter}
ggplot(data = pf, aes(x = age, y = friendships_initiated)) +
  geom_point() +
  xlim(13,90)
```

```{r}
ggplot(data = pf, aes(x = age, y = friendships_initiated)) +
  geom_jitter(alpha = 1/20) +
  xlim(13,90)
```

```{r}
ggplot(data = pf, aes(x = age, y = friendships_initiated)) +
  geom_point(alpha = 1/20, position = position_jitter(h = 0)) +
  
  coord_trans(y = "sqrt")
```

***

### Overplotting and Domain Knowledge
Notes:

***

### Conditional Means
Notes:
```{r}
library(dplyr)
filter()
group_by()
mutate()
arrange()
```

```{r Conditional Means}
pf_by_age <- group_by(pf, age)
f_by_age <- summarise(pf_by_age,
                      fc_mean = mean(friend_count),
                      fc_median = median(friend_count),
                      n = n())
f_by_age <- arrange(f_by_age, age)

head(f_by_age)

```

```{r %>%}
pf.new <- pf %>%
  group_by(age) %>%
  summarise(f_mean = mean(friend_count),
            f_median = median(friend_count),
            n = n()) %>%
  arrange(age)
```


Create your plot!

```{r}
qplot(x = age, y = fc_mean, data = f_by_age)
```


```{r Conditional Means Plot}
ggplot(f_by_age, aes(x = age, y = fc_mean)) +
  geom_line()
```

***

### Overlaying Summaries with Raw Data
Notes:

```{r Overlaying Summaries with Raw Data}
ggplot(pf, aes(age,friend_count)) +
  geom_point(alpha = 0.05, position = position_jitter(h = 0),
             color = 'orange') +
  #coord_trans(y = 'sqrt') +
  geom_line(stat = 'summary', fun.y = mean,
            color = 'blue') +
  geom_line(stat = 'summary', fun.y = quantile, 
            fun.args = list(probs = .1),
            linetype = 2, color = 'blue') +
  geom_line(stat = 'summary', fun.y = quantile,
            fun.args = list(probs = .9),
            linetype = 2, color = 'blue') +
  geom_line(stat = 'summary', fun.y = quantile,
            fun.args = list(probs = .5),
            color = 'blue') +
  coord_cartesian(xlim = c(13,90), ylim = c(0,1000))
```

#### What are some of your observations of the plot?
Response:

***

### Moira: Histogram Summary and Scatterplot
See the Instructor Notes of this video to download Moira's paper on perceived audience size and to see the final plot.

Notes:

***

### Correlation
Notes:

```{r Correlation}
cor.test(x = pf$age, y = pf$friend_count, method = 'pearson')
```
```{r}
with(pf, cor.test(age, friend_count, mehtod = 'pearson'))
```

```{r}
with(subset(pf, pf$age <= 70), cor.test(age, friend_count, mehtod = 'pearson'))
```

Look up the documentation for the cor.test function.

What's the correlation between age and friend count? Round to three decimal places.
Response:

***

### Correlation on Subsets
Notes:

```{r Correlation on Subsets}
with(                 , cor.test(age, friend_count))
```

***

### Correlation Methods
Notes:

***

## Create Scatterplots
Notes:

```{r}
cor.test(pf$www_likes_received, pf$likes_received)
```


```{r}
ggplot(pf, aes(x= www_likes_received, y = likes_received)) +
  geom_point(alpha = .05, position = position_jitter(),
             color = 'black')+
  coord_cartesian(xlim = c(0,1000), ylim = c(0,1000))


```


```{r}
ggplot(pf, aes(x= www_likes_received, y = likes_received)) +
  geom_point(alpha = .05, position = position_jitter(),
             color = 'black')+
  coord_cartesian(xlim = c(0,quantile(pf$www_likes_received, 0.95)), ylim = c(0,quantile(pf$likes_received, 0.95))) +
  geom_smooth(method = 'lm', color = 'red')

```

***

### Strong Correlations
Notes:

```{r Strong Correlations}

```

What's the correlation betwen the two variables? Include the top 5% of values for the variable in the calculation and round to 3 decimal places.

```{r Correlation Calcuation}

```

Response:

***

### Moira on Correlation
Notes:

***

### More Caution with Correlation
Notes:

```{r More Caution With Correlation}
install.packages('alr3')
library(alr3)
```

Create your plot!

```{r Temp vs Month}
data("Mitchell")

ggplot(Mitchell, aes(Month, Temp)) +
  geom_point()

```

***

### Noisy Scatterplots
a. Take a guess for the correlation coefficient for the scatterplot.

b. What is the actual correlation of the two variables?
(Round to the thousandths place)

```{r Noisy Scatterplots}
cor.test(Mitchell$Month, Mitchell$Temp)
```

***

### Making Sense of Data
Notes:

```{r Making Sense of Data}
Mitchell$Month <- (Mitchell$Month)%%12
head(Mitchell,25)
```

```{r}
ggplot(Mitchell, aes(Month, Temp)) +
  geom_point()
```

***

### A New Perspective

What do you notice?
Response:

Watch the solution video and check out the Instructor Notes!
Notes:

***

### Understanding Noise: Age to Age Months
Notes:

```{r Understanding Noise: Age to Age Months}
pf$age_with_months <- pf$age + 1 - pf$dob_month/12
```

***

### Age with Months Means

```{r Age with Months Means}
pf.fc_by_age_months <- pf %>%
  group_by(age_with_months) %>%
  summarise(fc_mean = mean(friend_count),
  fc_median = median(friend_count), 
  n = n()) %>%
  arrange(age_with_months)


```

Programming Assignment
```{r Programming Assignment}
ggplot(pf.fc_by_age_months, aes(age_with_months, fc_mean)) +
  geom_line() +
  coord_cartesian(xlim = c(13,71), ylim = c(0,500))
  

```

***

### Noise in Conditional Means

```{r Noise in Conditional Means}

```

***

### Smoothing Conditional Means
Notes:

```{r Smoothing Conditional Means}

```

***

### Which Plot to Choose?
Notes:

***

### Analyzing Two Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

